Modeling Bandwagoning and Hype in the MLB

### 2020-08-24 Paper_Outline.Rmd
Updated graphs

fig1_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_classic() +
  labs(main="Google Trend of Dodgers and Giants", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("dodgerblue", "darkorange"))
```

[Brief discussion: note how there are consistent phases of the season, 
but success strongly determines size of spike; e.g. Giants won in X years, 
Dodgers won in Y years]

@@

fig2a_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_classic() +
  labs(main="Google Trend of Dodgers and Giants", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("dodgerblue", "darkorange"))
```

@@

fig2b_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_classic() +
  labs(main="Google Trend of Dodgers and Cubs", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("firebrick2", "dodgerblue"))
```

@@

@@

>>>>

fig1_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_minimal() +
  labs(title="Google Trend of Dodgers and Giants", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("dodgerblue", "darkorange")) +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
```

  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())[Brief discussion: note how there are consistent phases of the season, 
but success strongly determines size of spike; e.g. Giants won in X years, 
Dodgers won in Y years]

@@

fig2a_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_minimal() +
  labs(title="Google Trend of Dodgers and Giants", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("dodgerblue", "darkorange")) +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
```

@@

fig2b_dat %>%
  ggplot(aes(x = as.Date(date), y = googlehits, group = team)) + 
  geom_line(aes(color = team)) + 
  theme_minimal() +
  labs(title="Google Trend of Dodgers and Cubs", x = "Date", y = "Google Hits") + 
  scale_color_manual(values=c("firebrick2", "dodgerblue")) +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

```

@@

```{r}
fig3_dat <- read.csv("combined_data.csv")

fig3_dat %>%
  ggplot(aes(x = googlehits)) + 
  geom_histogram(bins = 30,
                 col = "dodgerblue4",
                 fill = "dodgerblue",
                 alpha = 0.7) +
  theme_minimal() + 
  theme(axis.title.y=element_blank()) + 
  labs(title = "Google Trend Hits", x = "Google Hits")

```

```{r}
fig3_dat %>%
  ggplot(aes(x = log(googlehits))) + 
  geom_histogram(bins = 10,
                 col = "dodgerblue4",
                 fill = "dodgerblue",
                 alpha = 0.7) +
  theme_minimal() + 
  theme(axis.title.y=element_blank()) + 
  labs(title = "Google Trend Hits", x = "Google Hits")
```

@@

```{r}
fig4_dat <- read.csv("plotting_data.csv") %>%
  mutate(date = as.Date(date))

# giants - quantile normalized hits plot for last 5 years
fig4_dat %>%
  filter(team == "San Francisco Giants",
         date <= as.Date("2020-07-01") & date >= as.Date("2015-07-01")) %>%
  ggplot(aes(x = date, y = qn_ghits)) +
  geom_line(col = "darkorange") +
  theme_minimal() +
  labs(title = "San Francisco Giants") + 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

# giants - monthly average hits over ALL years with phases
fig4_dat %>%
  filter(team == "San Francisco Giants") %>% 
  group_by(month) %>%
  summarise(monthly_avg = mean(googlehits)) %>%
  ggplot(aes(x = as.factor(month), y = monthly_avg, group = 1)) +
  geom_point(col = "darkorange") +
  geom_line(col = "darkorange") + 
  theme_minimal() +
  geom_vline(xintercept = c(4,10), linetype = "dashed", color = "black") + 
  geom_text(aes(x=2, y=7, label = "Off-Season")) +
  geom_text(aes(x=11.5, y=7, label = "Off-Season")) +
  geom_text(aes(x=4, y=7, label = "Opening Day\n"), angle = 90) + 
  geom_text(aes(x=7, y=7, label = "Season")) + 
  geom_text(aes(x=10, y=7, label = "Post-Season\n"), angle = 90) + 
  labs(title = "Monthly Average of Google Trend Hits for SF Giants (2004 - Present)") + 
  scale_x_discrete(labels = month.abb[c(1:12)]) + 
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank())

```

```{r}
# Mariners - quantile normalized hits plot for last 5 years
fig4_dat %>%
  filter(team == "Seattle Mariners",
         date <= as.Date("2020-07-01") & date >= as.Date("2015-07-01")) %>%
  ggplot(aes(x = date, y = qn_ghits)) +
  geom_line(col = "cyan4") +
  theme_minimal() +
  labs(title = "Seattle Mariners") + 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
```
